New_Data_Coherence

### 2019-08-23 Analysis/Coherence_Calculations_New.Rmd
fix dplyr issue
add fully integrated coherence calculations file

string = string %>% dpyr::rename(hgnc_symbol_b = hgnc_symbol)

@@

#Read in KEGG pathways for coherence
msig = readRDS("KEGG_String.rds")
msig =msig %>% filter(Category == "CP:KEGG")
coherence_tab = bind_rows()
for (i in unique(dis_slopes_string_count$Disease)) {
  #Filter to only include specific disease coherence
  dis = dis_slopes_string_count %>% filter(Disease == i)

  #Get closest KEGG pathways in term of gene counts
  msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
  #Take top 10 KEGG pathways
  msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]

@@

      #Normalize based on random slope and the median of kegg slopes (More robust)
      coherence = (dis$Slope - rand_slope)/(median(msigs$Slope)-rand_slope)
      coherence = data.frame(Disease = dis$Disease, Coherence = coherence, Msig_Norm = median(msigs$Slope), Rand_Norm = rand_slope )      
      coherence_tab = bind_rows(coherence, coherence_tab)
      saveRDS(coherence_tab, "coherence_string.rds")
}

@@

      coherence = (dis$Slope - rand_slope)/(median(msigs$Slope)-rand_slope)
    coherence = data.frame(Disease = dis$Disease, Coherence = coherence, Msig_Norm = median(msigs$Slope), Rand_Norm = rand_slope )      
      coherence_tab = bind_rows(coherence, coherence_tab)
      saveRDS(coherence_tab, "coherence_string_filt.rds")
}

@@

      coherence = (dis$Slope - rand_slope)/(median(msigs$Slope)-rand_slope)
      coherence = data.frame(Disease = dis$Disease, Coherence = coherence, Msig_Norm = median(msigs$Slope), Rand_Norm = rand_slope )      
      coherence_tab = bind_rows(coherence, coherence_tab)
      saveRDS(coherence_tab, "coherence_biogrid.rds")
}

@@

      coherence = (dis$Slope - rand_slope)/(median(msigs$Slope)-rand_slope)
      coherence = data.frame(Disease = dis$Disease, Coherence = coherence, Msig_Norm = median(msigs$Slope), Rand_Norm = rand_slope )

@@

      coherence = (dis$Slope - rand_slope)/(median(msigs$Slope)-rand_slope)
      coherence = data.frame(Disease = dis$Disease, Coherence = coherence)

@@

#Read in old diseases/categories
# old_res = read.csv("./manuscript/supplementary_table_S1.csv") %>% dplyr::select(-Coherence.Biogrid, -Coherence.String.full, -Coherence.String.filt)

# #Read in old coherences
# old_coh = read.csv("./manuscript/supplementary_table_S1.csv") %>% dplyr::select(Disease = Trait, Coherence.Biogrid, Coherence.String.full, Coherence.String.filt)

#Bind old coherence to new for analysis
#test_coherence = left_join(coherence_full, old_coh)

#Replace trait with diseases for ease of combination
#colnames(old_res)[1] = "Disease"

#Join new and old results filtering NA SNPs (Non-shared traits)
#coherence_full = left_join(coherence_full, old_res) %>% filter(!is.na(Total.number.of.SNPs))

#Match original order
#coherence_full = coherence_full %>% dplyr::select(Disease, Category, Total.number.of.SNPs, Total.number.of.genes, Biogrid_Coherence, String_Coherence, String_Filt_Coherence, P.value.Biogrid, P.value.String.full, P.value.String.filt)

#Filter out forced . from read.csv
#colnames(coherence_full) = gsub("\\.", " ", #colnames(coherence_full))

#Replace _ with spaces for style
#colnames(coherence_full) = gsub("\\_", " ", #colnames(coherence_full))

#Rename to old first column name
#coherence_full = coherence_full %>% dpyr::rename(Trait = Disease)

#coherence_full[,5:7] = apply(coherence_full[,5:7], 2, function(x) ifelse(x<0, 0, ifelse (
  #x>1, 1, x
#)))

#Add reactome data

#coherence_full = left_join(coherence_full, coherence_biogrid_cc, by= c("Trait"= "Disease"))

#coherence_full = left_join(coherence_full, coherence_string_cc, by= c("Trait"= "Disease"))

#coherence_full = left_join(coherence_full, coherence_string_filt_cc, by= c("Trait"= "Disease"))

#coherence_full = left_join(coherence_full, coherence_biogrid_react, by= c("Trait"= "Disease"))

#coherence_full = left_join(coherence_full, coherence_string_react, by= c("Trait"= "Disease"))

#coherence_full = left_join(coherence_full, coherence_string_filt_react, by= c("Trait"= "Disease"))

#coherence_full = coherence_full %>% dpyr::rename(`Biogrid Coherence Reactome` = Coherence.x, `String Coherence Reactome` = Coherence.y, `String Filt Coherence Reactome` = Coherence.x.x, `Biogrid Coherence CC` = Coherence.y.y, `String Coherence CC` = Coherence.x.x.x, `String Filt Coherence CC` = Coherence.y.y.y)

#Move p-values to end
#coherence_full = coherence_full %>% dplyr::select(Trait:`String Filt Coherence`,`Biogrid Coherence Reactome`:`String Filt Coherence CC`)

#Commented out old results for final version

# coherence_full = left_join(coherence_full, old_coh, by = c("Trait" = "Disease"))
# 
# colnames(coherence_full)[14:16] = c("Biogrid Coherence Old", "String Coherence Old", "String Filt Coherence Old")
# 
# coherence_full = coherence_full[, c(1:10, 14,16,15, 11:13)]
# 
# coherence_no_big = coherence_full %>% filter(Trait != "Height") %>% filter(Trait != "Obesity-related traits")

@@

```{r}
write.csv(coherence_full %>% arrange(`Category`, `Trait`), "Coherence_New.csv", row.names = FALSE)

```{r}
msig_sum = readRDS("KEGG_String.rds") %>% distinct() %>% filter(!grepl("_1", Category))

msig_slopes =msig_sum %>% group_by(Category) %>% summarise(`Mean Slope` = mean(Slope, na.rm = TRUE))

write.csv(msig_slopes, "./tables/Category_Slopes.csv", row.names = FALSE, col.names = TRUE, quote = FALSE)
```

@@

write_xlsx(coherence_disease, "./tables/supplementary_table_S1.xlsx")

>>>>

string = string %>% dplyr::rename(hgnc_symbol_b = hgnc_symbol)

@@

#Read in KEGG pathways for coherence
msig = readRDS("KEGG_String.rds")
msig =msig %>% filter(Category == "CP:KEGG")
coherence_tab = bind_rows()
for (i in unique(dis_slopes_string_count$Disease)) {
  #Filter to only include specific disease coherence
  dis = dis_slopes_string_count %>% ungroup() %>% filter(Disease == i)
  #Get closest KEGG pathways in term of gene counts
  msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
  #Take top 10 KEGG pathways
  msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]

@@

      #Normalize based on random slope and the median of kegg slopes (More robust)
      coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
      coherence = data.frame(Disease = dis$Disease, Coherence = coherence, Msig_Norm = median(msigs$Slope, na.rm = TRUE), Rand_Norm = rand_slope )      
      coherence_tab = bind_rows(coherence, coherence_tab)
      saveRDS(coherence_tab, "coherence_string.rds")
}

@@

      coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
    coherence = data.frame(Disease = dis$Disease, Coherence = coherence, Msig_Norm = median(msigs$Slope, na.rm = TRUE), Rand_Norm = rand_slope )      
      coherence_tab = bind_rows(coherence, coherence_tab)
      saveRDS(coherence_tab, "coherence_string_filt.rds")
}

@@

      coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
      coherence = data.frame(Disease = dis$Disease, Coherence = coherence, Msig_Norm = median(msigs$Slope, na.rm = TRUE), Rand_Norm = rand_slope )      
      coherence_tab = bind_rows(coherence, coherence_tab)
      saveRDS(coherence_tab, "coherence_biogrid.rds")
}

@@

      coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
      coherence = data.frame(Disease = dis$Disease, Coherence = coherence, Msig_Norm = median(msigs$Slope, na.rm = TRUE), Rand_Norm = rand_slope )

@@

      coherence = (dis$Slope - rand_slope)/(median(msigs$Slope, na.rm = TRUE)-rand_slope)
      coherence = data.frame(Disease = dis$Disease, Coherence = coherence)

@@

@@

@@

require(writexl)
write_xlsx(coherence_disease, "./tables/supplementary_table_S1.xlsx")
